\documentclass[mathpazo]{cicp}

%\journal{Applied Mathematics and Computation}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsrefs}
%\usepackage{subfig}

\begin{document}

%\title{\emph{hp}-Finite Element Model of Poisson and Nernst-Planck\\ System of Equations}
\title{Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM}


\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{4},
Pavel Solin\affil{2}\comma\affil{3}\comma\corrauth,
Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{4}}

\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{2}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{3}\ Institute of Thermomechanics, Prague, Czech Republic\\
\affilnum{4}\ Institute of Technology, Tartu University, Estonia}

\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}

%\author[unrme,tartu]{D.~Pugal}
%\ead{david.pugal@gmail.com}
%
%\author[unrmath,czech]{P.~Solin\corref{cor2}}
%\ead{solin@unr.edu}
%
%\author[unrme]{K.~J.~Kim\corref{cor1}}
%\ead{kwangkim@unr.edu}
%
%\author[tartu]{A.~Aabloo}
%\ead{alvo@ut.ee}
%
%\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
%\address[unrmath]{Department of Mathematics and Statistics,
%University of Nevada, Reno, NV, U.S.A.}
%\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
%\address[tartu]{Institute of Technology, Tartu University, Estonia}
%
%\cortext[cor1]{Corresponding author}
%\cortext[cor2]{Principal corresponding author}

\begin{abstract}
We are concerned with a model of ionic polymer-metal composite (IPMC) materials
that consists of a coupled system of the Poisson and Nernst-Planck equations, 
discretized by means of the finite element method (FEM). We show that due to the 
transient character of the problem it is efficient to use adaptive algorithms 
that are capable of changing the mesh dynamically in time. We also show 
that due to large qualitative and quantitative differences between the 
two solution components, it is efficient to approximate them on different 
meshes using a novel adaptive multimesh \emph{hp}-FEM. The study is 
accompanied with numerous computations and comparisons of the adaptive 
multimesh \emph{hp}-FEM with several other adaptive FEM algorithms. 
\end{abstract}

%\begin{keyword}
%\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
%finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
%\end{keyword}

%see http://www.ams.org/mathscinet/msc/msc2010.html?t=35Qxx&btn=Current

\ams{35Q84, 35Q05, 35J47}
\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
finite element method, FEM, adaptive multimesh \emph{hp}-FEM }
\maketitle


%\end{frontmatter}

\input{intro}
\input{motivation}
\input{model}
\input{results}
\input{conclusions}

\section*{Acknowledgments}
The second author was partially supported by the Grant Agency of the Academy of 
Sciences of the Czech Republic under Grant No. IAA100760702, and by the U.S.
Department of Energy Research Subcontract No. 00089911. 
The third author acknowledges the financial support of the U.S. Office of Naval Research 
under Award N000140910218. The fourth author acknowledges the financial support of
the Estonian Ministry of Education, grant \#SF0180008s08.

%\begin{thebibliography}{99}
%\bibitem{\ldots}..

%\end{thebibliography}
\newpage

\bibliographystyle{amsrn}    % Bibliography: Author-Date system
\bibliography{pugal-esco2010}      % pls. call your database here

\end{document}


